### 2021-11-18 documentos/pce.tex
para revisar linea

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The first one is needed to
send convex combinations of density matrices into the convex combinations of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving is required for the process $\mcE$ to be deterministic, this
is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
happen with probability equal to one. The complete
\subsection{Quantum channels} % {{{ Quantum channels comprehend the most
general linear operations that a quantum system undergo independently of its
past~\cite{zimansbook,cirac}. To introduce their construction and properties,
first let us define several objects. We will denote Hilbert spaces as \hilbert
and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded
operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$,
the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset
of the so called trace-class operators $\mcT(\hilbert)$, for the finite
dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$
coincide~\cite{zimansbook}.

>>>>

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The first one is needed to
send convex combinations of density matrices into the convex combinations of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving is required for the process $\mcE$ to be deterministic, this
is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
happen with probability equal to one. The complete
